Bicycle Balance Assistance Reduces Probability of Falling at Low Speeds When Subjected to Mechanical Perturbations

### 2024-05-29 main.tex
Added some of the static figures.

\begin{figure}
  \centering
  % TODO : scale these pngs to a reasonable size for an A4 sheet
  %\subcaptionbox{}{\includegraphics[width=70mm]{figures/participant-in-set-up.png}}
  \subcaptionbox{}{\includegraphics[width=70mm]{example-image-a}}
  %\subcaptionbox{Diagram of perturbation system.}{\includegraphics[width=70mm]{figures/setup-diagram.png}
  \subcaptionbox{Diagram of perturbation system.}{\includegraphics[width=70mm]{example-image-b}
}
\end{figure}

@@

\begin{figure}
  \includegraphics{example-image-a}
  \caption{Thesis Fig 5.1 on pg 37}
\end{figure}

>>>>

\begin{figure}
  \centering
  % TODO : scale these pngs to a reasonable size for an A4 sheet
  \subcaptionbox{}{\includegraphics[width=70mm]{figures/participant-in-set-up.png}}
  \subcaptionbox{Diagram of perturbation system.}{\includegraphics[width=70mm]{figures/setup-diagram.png}
}
\end{figure}

@@

\begin{figure}
  \centering
  \subcaptionbox{Start}{\includegraphics[width=60mm]{figures/start.png}}
  \subcaptionbox{During}{\includegraphics[width=60mm]{figures/during.png}}
  \subcaptionbox{After}{\includegraphics[width=60mm]{figures/after.png}}
  \subcaptionbox{Recovery}{\includegraphics[width=60mm]{figures/recovery.png}}
  \caption{Thesis Fig 5.1 on pg 37}
\end{figure}
